---
title: "Getting started"
author: "Daniel Ebbert"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(knitr)
```

This vignette describes how to get started using the opencastR package.

## Setup

In order to use the opencastR package the hostname of your Opencast server, your username and password need to be set as environment variables. For this example I use the Legacy Opencast Testserver and the default credentials.

```{r oc_setup}
library(opencastR)

Sys.setenv(OPENCAST_HOST = "https://legacy.opencast.org")
Sys.setenv(OPENCAST_USERNAME = "admin")
Sys.setenv(OPENCAST_PASSWORD = "opencast")
```

## First call

To check if everything is setup correctly the oc_api function can be used which returns the default api version and the server url.

```{r oc_api}
oc_api()
```

The return of this functions shows that a list of the class *opencast_api* has been returned. This list contains three elements. The content, the url that was called and the full response. So access only the content we can do the following.

```{r oc_api_content}
api_test <- oc_api()
api_test$content
```

## Events

To showcase a more useful functions a list of events on the testserver can be retrieved.

```{r oc_events_content}
events <- oc_list_events()
kable(events$content)
```
